---
title: "Creating a Round Robin Meeting Schedule"
author: "John Lepird"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating a Round Robin Meeting Schedule}
  %\VignetteEngine{knitr::rmarkdown}
  \VignetteEncoding{UTF-8}
---

This vignette demonstrates how to use the `raml` package to solve a simple scheduling problem: twelve representatives attend a conference, and each representative needs to meet every other representative one on one. How can we most efficiently schedule this conference?

To begin, we define the model object:

```{r}
library(raml)

m <- Model()
m$sense <- "min"
```

Now, we define our decision variables: should representative `i` meet with representative `j` during time period `k`?

```{r}
m$var(x[1:12, 1:12, 1:20], "Binary")
```

We know that if `i` is meeting with `j`, then `j` must also be meeting with `i`:

```{r}
for (k in 1:20) { 
  for (i in 1:12) {
    for (j in 1:i) {
      m$constraint(x[i, j, k] == x[j, i, k])
    }
  }
}
```

Furthermore, each representative can only meet with one other representative during a given time frame:

```{r}
for (k in 1:20) {
  for (i in 1:12) {
    m$constraint(rsum(x[i,j_i,k], j_i = 1:12) <= 1)
  }
}
```

Now, we require every representative meet with every other representative: 

```{r}
for (i in 1:12) {
  for (j in 1:12) {
    if (i != j) {
      m$constraint(rsum(x[i,j,k_i], k_i = 1:20) >= 1)
    }
  }
}
```

We define our objective function to minimize the amount of time everyone has to spend at the conference:

```{r}
gamma <- 1.1
m$objective(rsum(gamma^k_i * x[i_i, j_i, k_i], i_i = 1:12, j_i = 1:12, k_i = 1:20))
```

Finally, we can solve the model:

```{r}
m$solve()
```

Now, we can visualize the meetings:

```{r, fig.show='hold', fig.cap = "Conference Schedule.", fig.height=5, fig.width=5}
df <- data.frame(i = numeric(), j = numeric(), k = numeric())
for (i in 1:12) {
  for (j in 1:12) {
    for (k in 1:20) {
      if (value(x[i,j,k]) > 0) {
        df <- rbind(df, data.frame(i = i, j = j, k = k))
      }
    }
  }
}
library(ggplot2)
ggplot(df, aes(i,j, label = k)) + 
  geom_text() + 
  scale_x_continuous("Rep i", breaks = 1:12) + 
  scale_y_continuous("Rep j", breaks = 1:12) + 
  ggtitle("When should Rep i meet with Rep j?") + 
  theme_minimal()
```
